The Current State of R Tools for Nonlinear Least Squares Modeling

### 2023-07-03 RefactoringNLS/revision202307/StateOfRToolsForNLS.Rmd
update to work

The complexity of this object is a challenge to users. Let us use the
`result` as the returned object from `nls()`, `minpack.lm::nlsLM()` or,
`gslnls::gsl_nls()`. For example, the `data` return element is an R symbol. To
actually access the data from this element, we need to use the syntax:
```
eval(parse(text=result$data))
```
However, if the call is made with `model=TRUE`, then there is a returned element
`model` which contains the data, and we can list its contents using:
```
ls(result$model)
```
and if there is an element called `xdata`, then it can be accessed as
`result$model$xdata`.

By contrast, `nlsr::nlxb()` returns a much simpler structure of 11 items
in one level. Moreover, `nlxb` explicitly returns the sum of squares, the 
residual vector, Jacobian, and counts of evaluations.

>>>>

The complexity of this object is a challenge to users. Let us use the
`result` as the returned object from `nls()`, `minpack.lm::nlsLM()` or,
`gslnls::gsl_nls()`. For example, the `data` return element is an R symbol. 
If the user's environment exists, which it may not, we could see this data 
via the syntax:
```
eval(parse(text=result$data))
```
However, a better approach is to make the call to `nls()` with `model=TRUE`, 
which returns an element 
`model` which contains the data, and we can list its contents using:
```
ls(result$model)
```
and if there is an element called `xdata`, then it can be accessed as
`result$model$xdata`.

By contrast, `nlsr::nlxb()` returns a much simpler structure of 11 items
in one level. Moreover, `nlxb` explicitly returns the sum of squares, the 
residual vector, Jacobian, and counts of evaluations, but does not include
the input data.
